\textbf{Autoreduction - an automated data reduction system for beamline instruments at the ISIS Facility}

### 2017-07-12 Documentation/paper/paper.tex
Updated state database section

A node keeps track of the status of jobs in a local SQL database. This
server hosts a Python service responsible for listening on \emph{Data
Ready}, to create new jobs in the database and then dispatch them to \emph{Reduction
Pending}. It manages variables for reduction, and selects the correct
set for the job. The same server is also responsible for serving the
Python/Django\cite{django} web app, and the database is accessible through
Django's object interface.

The daemon receives status updates from reduction workers on
\emph{Reduction Started}, \emph{Reduction Complete} and \emph{Reduction
Error}, making the appropriate changes to the database. On some messages
in the error queue, the daemon will create and schedule the appropriate
retry runs. A system for emailing notifications of run failures to
administrators is also implemented here.

>>>>

The \emph{QueueProcessor} service runs as a daemon and is the service responsible
for keeping track of the status of jobs in an SQL database. The service
listens on the \emph{Data Ready} queue. When messages are first received,
the service will set the correct variables for the job, create new jobs in 
the database and, when ready, will send a message to the \emph{Reduction Pending} queue.

The daemon service also receives updates from the reduction worker itself. When the 
reduction worker reaches certain stages of its execution, it will send messages to
\emph{Reduction Started}, \emph{Reduction Complete} and \emph{Reduction Error}.
The \emph{QueueProcessor} service also listens on these queues and will update the database
accordingly when messages are received. For some messages in the error queue, the daemon 
will create and schedule the appropriate retry runs. There is also a system in place for 
emailing notifications of run failures to administrators.

Since the database is being frequently being updated throughout the process of autoreduction,
the Python/Django\cite{django} WebApp is always up to date with the latest information.
This means that users can easily check on the progress of their runs and get a good idea of 
how long it is going to take for them to retrieve their data at the end.
